Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-09-30 ms.tex

\begin{figure}[ht!]
\epsscale{0.5}
%% XXX--ugh, so these have enough points that they take forever to render. Thoughts on how to improve welcome
%\plotone{plots/sats_slv1.pdf}
%\plotone{plots/sats_slv2.pdf}
%\plotone{plots/sats_ow.pdf}
\epsscale{1}
\caption{Hammer projection of the altitude and azimuth positions of our simulated satellite constellations as seen from Rubin Observatory on October 1, 2023 with a sun altitude of -18 degrees. Red points show un-illuminated satellites, blue points show those illuminated by the sun, and black points are illuminated and above the Rubin altitude limit. \label{fig-simulated-constellations}}
\end{figure}

>>>>

\begin{figure}[ht!]
\epsscale{0.35}
%% XXX--matplotlib seems to like leaving a huge bounding box buffer around 
\plotone{plots/sats_slv1.pdf}
\plotone{plots/sats_slv2.pdf}
\plotone{plots/sats_ow.pdf}
\epsscale{1}
\caption{Hammer projection of the altitude and azimuth positions of our simulated satellite constellations as seen from Rubin Observatory on October 1, 2023 (sun altitude -18 degrees). Red points show un-illuminated satellites, blue points show those illuminated by the sun, and black points are illuminated and above the Rubin altitude limit. \label{fig-simulated-constellations}}
\end{figure}
